---
title: "Alcohol vs Seat choice"
author: "Connor Rice"
date: "Fall 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

$H_0$: There is no difference between the average number of drinks imbibed between people conditioned on the row they sit in.

$H_A$: The average number drinks is different between at least two rows. 

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

The median and quartile ranges for both front and middle seats were extremely close to one another, however the median and quartile ranges for people in back seats were significantly higher than those sitting in the front or middle seats. This indicates a higher average consumption of alcohol by those in the back seats, though all the seat types had large outliers beyond their quartile ranges.

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```

The middle row(s) had the largest sample size but had a significantly lower average amount of alcohol consumed than the back row and slightly higher than those in the front seats. The back row seats had by far the highest average alcohol consumption, the middle seats about one third the mean of the back row seats, and the front row seats about one half the mean of the middle row seats indicating a trend of increase in alcohol consumption the further back the subjects sat.

## Inferential Tests

## Conclusions


